---
title: "Analysis"
author: "Pranay Gundam"
date: "`r Sys.Date()`"
output: html_document
---

# State Name Etymology

First as some color commentary for this first TidyTuesday analysis. This data 
set doesn't give one much to work with. There are some interesting 
visualizations one can make, but I found it quite difficult to ask any 
meaningful well conditioned research questions. That being said the best I could
think of for now was: The effects of native american vs european influence on
states.

The influence of Native American vs European culture is not a very concrete 
term. In the context of this project, we will be using the etymology of a 
state's name as a proxy for Native American vs European influence on a state. 
This is of course not anywhere near perfectly analogous but gives some level of
insight about the early formation of a given state.


```{r}
library(tidyverse)
```


```{r}
states = read_csv("states.csv")
etymo = read_csv("state_name_etymology.csv")
```


The states dataset is 

```{r}

mergedf = merge(states, etymo, by = "state")

head(mergedf)
```

```{r}
unique(mergedf$language)
```

```{r}
mergedf %>%
  ggplot(aes(x = date_named, y = population_2020)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm")
  
  
mergedf %>%
  ggplot(aes(x = admission, y = population_2020)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm")
```

```{r}
namedPop = lm(data = mergedf, formula = population_2020 ~ admission)
summary(namedPop)
```

```{r}

```


One interesting question could be the differences in state formation and current
population between states with native American origins vs European origins which
we will use the etymology of their state name






