---
title: "State Names"
author: "Pranay Gundam"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

# State Name Etymology

First as some color commentary for this first TidyTuesday analysis. This data 
set doesn't give one much to work with. There are some interesting 
visualizations one can make, but I found it quite difficult to ask any 
meaningful well conditioned research questions. That being said the best I could
think of for now was: The effects of native american vs european influence on
states.

The influence of Native American vs European culture is not a very concrete 
term. In the context of this project, we will be using the etymology of a 
state's name as a proxy for Native American vs European influence on a state. 
This is of course not anywhere near perfectly analogous but gives some level of
insight about the early formation of a given state.

```{r, include=FALSE}
library(tidyverse)
```
```{r, include=FALSE}
states = read_csv("states.csv")
etymo = read_csv("state_name_etymology.csv")
```

### EDA

There are originally two datasets that we combine together which in total has
information on simple characteristics of each state such as its' population in 
2020, number of representatives in the House of Representatives, land/water
area metrics, and etymological characteristics of a states' name. Currently 
there are various languages and we characterize them into European or not.

```{r}
mergedf = merge(states, etymo, by = "state")

eurolang = function(x){
  y = substring(x, 1, 8)
  return(grepl("Spanish", y, fixed=TRUE) |
         grepl("English", y, fixed=TRUE) |
         grepl("Latin", y, fixed=TRUE) |
         grepl("Russian", y, fixed=TRUE) |
         grepl("French", y, fixed=TRUE) |
         grepl("Greek", y, fixed=TRUE) |
         grepl("Dutch", y, fixed=TRUE))
}

findf = mergedf %>%
  mutate(eurolang = ifelse(eurolang(language), 1, 0))
```

After doing so, we can see that the division between these two classes of 
languages is close to even. 26 European languages and 30 non-European languages.

### Main Analysis

For the first TidyTuesday we are keeping things simple and just creating a fixed
effects model to determine if having a european vs native american origin has an 
effect on the population of a state in 2020 controlled by its land size, water
size and the date at which the state's name was decided. Our regression looks
like 

$$pop = \beta_0 + \beta_1X_{origin} + \pmb{\beta}Z + \epsilon.$$

Our data set doesn't give a very clear variable to indicate if a state is of 
european native american origin but we will be using the etymology of a 
state's name as a proxy for its origin.


```{r}
model = lm(data = findf, formula = population_2020 ~ admission + date_named + 
             land_area_km2 + water_area_km2 + eurolang)
summary(model)
```

The results indicate that there isn't any statistically significant effect of 
the eurolang variable (and therefore our proxy for the cultural origins of a 
state) on the population of a state in 2020. As an explanation for our result, 
other than the obvious potential explanation that there simply is no 
relationship between the two it could also be that the amount of time that has 
passed since the founding of a state has overturned any residual effects of its
cultural founding.

We should obviously discuss some limitations of the discussion above. There
are undoubtedly some un-tracked variables that could contribute to omitted 
variable bias: for example, it is likely that the distance to a body of water
and ports is connected to both the population in that state and the etymological
origins of that state (since these are the states that were often colonized 
first by europeans).

In addition, the relationship between the etymology of a state's name and it's
cultural origins may not be a strong link which would make the supposed
causal relationship we are trying to discern between the cultural origins of a 
state and its population in 2020 not the relationship we are exploring.

## Future TidyTuesday Posts

This current post personally feels a bit lackadaisical in terms of what I am 
actually doing but I just wanted to get one out the door and I have to start 
somewhere before I can release a product that is something I've worked on only 
for a week and I am also satisfied with.

Future posts, conditional on the specific data set that we are working with and
the type of questions we can ask, will range from building machine learning 
models to questions about causality or forecasting. Also, as a preface for the 
next two posts, the data sets we will be using are regarding spam emails and 
fair use cases. 
