---
title: "State Names"
author: "Pranay Gundam"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

# Fair Use Cases

This data set contains 251 legal cases regarding fair use law. There are a few
observed variables, but not enough to make a convincing predictive model to 
determine if a case would lean one way or the other (as was my initial thoughts 
when taking an initial look at this data set). 

## EDA

```{r, message=FALSE, output=FALSE}
library(tidyverse)
cases = read_csv("fair_use_cases.csv")
findings = read_csv("fair_use_findings.csv")

```


% Make a bar chart of ruling counts
```{r}
num_cases = cases %>%
  mutate(fair_use_found_num = ifelse(fair_use_found, 1, 0)) %>%
  group_by(year) %>%
  summarize(total_cases = n(),
            fair_use_found_sum = sum(fair_use_found_num),
            percent_fair = fair_use_found_sum/total_cases) %>%
  pivot_longer(cols = c(total_cases, fair_use_found_sum, percent_fair))

num_cases_per = num_cases %>%
  subset(name == "percent_fair")

num_cases %>% 
  ggplot(aes(x = year, y = value, color = name))+
  geom_line()
  
num_cases_per %>% 
  ggplot(aes(x = year, y = value))+
  geom_line()+
  geom_smooth()

```


% Make a summary table of all the counts of each tag of cases

```{r}
tag_count = cases %>%
  select(c("year", "categories")) %>%
  separate_wider_delim(cols = "categories", delim = c("; "), 
                       names = c("tag1", "tag2", "tag3", "tag4", "tag5"),
                       too_few = "align_start") %>%
  pivot_longer(cols = c("tag1", "tag2", "tag3", "tag4", "tag5")) %>%
  na.omit() %>%
  group_by(value) %>%
  summarize(tag_count = n())

tag_count
```


% Make a histogram of cases per year

```{r}
case_count = cases %>%
  mutate(fair_use_found_num = ifelse(fair_use_found, 1, 0)) %>%
  group_by(year) %>%
  summarize(total_cases = n())

case_count %>%
  ggplot(aes(x = year, y = total_cases))+
  geom_bar(stat = "identity", alpha = 0.6, fill = "darkgreen")+
  labs(x = "Year", y = "Count")

case_count_ext = cases %>%
  mutate(fair_use_found_num = ifelse(fair_use_found, 1, 0)) %>%
  group_by(year) %>%
  summarize(total_cases = n(),
            fair_use_found = sum(fair_use_found_num),
            fair_use_not_found = total_cases - fair_use_found) %>%
  select(-c(total_cases)) %>%
  pivot_longer(cols = c(fair_use_found, fair_use_not_found))

case_count_ext %>%
  ggplot(aes(x = year, y = value, fill = name))+
  geom_bar(stat = "identity", alpha = 0.6)+
  labs(x = "Year", y = "Count")
```





