\section{Weekly Summary}

\begin{tcolorbox}[colback=yellow!10,colframe=black!50,title=AI-Generated Content]
\noindent The summary below was written by Claude (Anthropic) from that week's regression outputs and series descriptions. It has not been reviewed or fact-checked by a human, and should be read as an automated, informal recap -- not analysis.
\end{tcolorbox}

Welcome back to the only weekly newsletter brave enough to shove economic time series into a blender and pretend the resulting smoothie means something. As always, the machine grabbed some random pairs from FRED, ran a line through them, and dared us to feel emotions about the R-squared. We complied. Standard disclaimer, delivered with the enthusiasm of a flight attendant on their eighth leg of the day: these are randomly paired series, there is no causal claim here, and spurious correlation isn't the bug, it's the entire personality of the project.

Monday kicked things off by pairing the Fed's holdings of medium-term Treasury securities with a discontinued Consumer Price Index for services in the South. The raw regression came in with a beefy R-squared of 0.77 and a p-value with enough zeros after the decimal to make you nervous, which is exactly the kind of thing that gets a lesser blog very excited. But then we detrended it, and the R-squared quietly deflated to 0.37 and, notably, the sign of the relationship flipped from positive to negative. Nothing says "we were just both drifting upward through history like two strangers on the same escalator" quite like a relationship that reverses direction the moment you take away its trend. A trend mirage, dabbed gently with a napkin.

Tuesday, however, is where I have to put down my sarcasm mug for a second. We regressed "Nonfinancial Noncorporate Business withdrawals from income of quasi-corporations" (a phrase I am legally required to read in one breath) against depreciation of nonresidential structures, and the raw R-squared was a frankly obscene 0.98. Fine, whatever, big numbers drift together, we've seen this movie. Except after detrending it STAYED at 0.87 with a p-value that is essentially a rounding error away from zero, and the coefficient barely budged from 0.42 to 0.40. That is genuinely the rare "this might actually be a real relationship" case, and honestly it's not insane that two measures of how much big physical business assets are wearing down and being paid out would move together. I'm not saying I've discovered anything. I'm saying the machine stumbled into something that survived the interrogation, and that's practically a holiday around here.

The back half of the week returned us to our regularly scheduled nonsense. Wednesday matched the resident population of Nuckolls County, Nebraska against a medical price index for congenital anomalies, posting a gorgeous raw R-squared of 0.88 that collapsed to 0.36 once detrended, i.e., "Nuckolls County shrinking and medical prices rising both happen over time, film at eleven." And Thursday achieved the impressive feat of being unconvincing in both directions: net unilateral transfers versus the number of failed banking institutions gave us a raw R-squared of 0.005 (a rounding error wearing a trench coat) that then, absurdly, became slightly significant after detrending with an R-squared of 0.08. So one day flatlines completely, the next its detrended residuals perk up just enough to be statistically annoying without being interesting. In summary: one relationship worth an eyebrow raise, three worth a shrug, and zero worth building a policy around. See you next week, when the blender goes again.
